---
title: "Project #3 Example"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    theme: cosmo
runtime: shiny_prerendered
---

```{r setup_python_project_3, include=FALSE}
library(learnr)
library(gradethis)
library(reticulate)
source('login_info.R')
# Change title of code editor boxes
tutorial_options(exercise.cap = "Execute Your R Code Below", exercise.checker = gradethis::grade_learnr)
# Set a max 15 second timer on executing code within code editor boxes
exercise.timelimit=15
```


## Example

This is an example made by Riccardo (Ricky) Esclapon for his application to the RStudio 2020 internship. The full document to go along with this small example can be found here: http://ricky-rstudio-internship-application.org/

Below is an example using learnr with both R and Python.

```{r}
print('this is R code')
```


```{python}
print('this is Python code')
```

### Python Exercise

This feature is not a feature that is available in the normal version of `learnr` and I am watching this repository for updates, where this code was originally sourced from: https://github.com/rstudio/learnr/pull/310

```{python exercise_chunk_py, exercise = TRUE}
# if running in R, this should return 10
# if running in Python, this should return FALSE and 5
x = 5
x <-10
print(x)
```

For this example of an interactive code chunk using Python I installed the forked version of learnr by user **[zoews](https://github.com/zoews)**: https://github.com/zoews/learnr

Can't wait for this feature to be integrated into the [standard version of learnr](https://github.com/rstudio/learnr)!

One more example hidden below, press the button to continue.

### Example R exercise With Code Check

Enter **4\*13** in the exercise below and press on the blue ***Submit Answer*** button:

```{r exercise_example, exercise=TRUE}
1 + 1
```

```{r exercise_example-solution}
4 * 13
```

```{r exercise_example-check}
grade_result(
  pass_if(~ identical(.result, 52), "This was an example for Ricky's RStudio Internship."),
  fail_if(~ identical(.result, 2), "Remember to replace 1 + 1 with 4 * 13 before submitting the answer.")
)
```



## More examples

### More Python:

```{python}
import shrimpy

public_key = r.shrimpy_public
secret_key = r.shrimpy_secret
client = shrimpy.ShrimpyApiClient(public_key, secret_key)
ticker = client.get_ticker('binance')
print(ticker)
```



